### 2016-04-06 Projects/DelCo_2012/Report/DelCo_2012.tex
Added fuel description for 2 story structure in CAFs report

The fuel load for two of the experiments consisted of 3 sofas, carpet, padding, and oriented strand board (OSB) paneling along the East, West, and South walls and ceiling. The three couches are aligned along the West wall and spaced 1.2~m (4~ft) apart. The specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:furniture_2story}. In total, this fuel package contains approximately {\bf XXX} fuel consisting of wood, polyurethane (PU), polyester (PET),and polyprolene (PP).

>>>>

The fuel load for two of the experiments consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (559~ft$^2$) of carpet and padding; and approximately 38 sheets of oriented strand board (OSB) paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the East, West, and South walls and ceiling. The three couches are aligned along the West wall and spaced 1.2~m (4~ft) apart. The specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:furniture_2story}. In total, this fuel package was composed of wood, polyurethane (PU), polyester (PET),and polyprolene (PP).
